\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-04-01 doc/response_2_reviews_Ecography1.txt

In lines 150 and 152 authors use term "correlate". I know that statistical models are often called correlative models in ecology but it is typically wrong and at least impresice. Hence, I would describe in more detail how the model inference was done - maximum likelihood, Bayesian inference or least squares or what.

RESPONSE: We replaced "correlated" with regressed. Details on the regression models are provided in Appendix A.

The description of the simulation study should include the specific values used for the simulator. Authors should also tell more clearly are their results from single simulation or from several simulations. Moreover, it would be good to know how sensitive the results are to the chosen simulator parameters. That is, if the simulated dynamics was made faster/slower and the interspecific interactions and dispersal made stronger/weaker how would the results change. This kind of "sensitivity" test would provide information about the generality of the results and insight on for which kind of real systems they might apply.

RESPONSE:
Both reviewers raised concerns about the lack of sensitivity analyses and the robustness of our results. We take these concerns seriously and have responded in a number of ways. 	1) We added new material and references to the Introduction to emphasize that our simulations are motivated by empirical examples in which spatial and temporal models detect different relationships between an environmental driver and an ecological response. Any difference in magnitude or sign in these relationships will lead to contrasting forecasts. This situation appears quite frequently in the empirical literature; it is not a theoretical curiosity. The purpose of our simulations is not to convince readers that this situation might possibly occur (we already know it does), but rather to demonstrate how this situation may arise and the challenges and opportunities it presents for ecological forecasting. Given the generality of the motivating empirical pattern, and the fact that we designed our case study to reproduce that pattern, and that the signal to noise ratio in our simulation is high, we do not believe that a detailed sensitivity analysis is necessary. However, we do agree with the reviewer that understanding how different parameters influence the rate of the shift in model weights is an important goal for future research. Fig. 6 seeks to make that point, but a more rigorous analysis is beyond the scope of this study.
	2) We have added supplementary tables showing parameter values for both case studies. 
	3) We now clarify that the results are based on one simulation run, but qualitative results were consistent.
	4) We have added more detail to the meta-community model description in Appendix B. We believe the description of the evo-evo model is quite complete (Appendix C), but would be happy to add more detail in response to specific questions. 
	5) We addressed Reviewer 2's question about nonstationarity (see below).

@@

Reviewer: 2

Comments to the Author
The manuscript asks an interesting question - is it better to use (short) time series or space-for-time substitutions. The results make intuitive sense, but they are difficult to judge because the manuscript does not give enough details about the work. There are no details about the simulations - how many years were simulated? What spatial extent? What parameter values were used? How was the (simulated) data collected? How many replicate simulations were run (if one, why were you unable to run more than one? How are we meant to know if the results replicate?)? etc. etc. Basically, it is impossible to re-create these analyses from the description. I would strongly suggest having separate Methods and Results sections, as this makes it easier to follow the description of the work (and also helps you focus on describing the methods, and the results).

RESPONSE: Our response to Reviewer 1's similar concerns addresses many of these points. We originally considered separate Methods and Results sections, but found that structure awkward given our two case studies. We could add Methods and Results subheaders within each of the case study sections if the editor and reviewers think that would be helpful.

@@

Beyond the writing, I think one important issue is the assumption of stationarity. My guess (and I have to guess, because we're not given this information) the spatial data is taken after the simulation has run to equilibrium. But what happens if the spatial data is taken when the climate is changing? I think that would be the important question for researchers using space-for-time with contemporary data.

RESPONSE: Interesting question! We modified our code for the community turnover example to study the situation in which temperature increases through the entire simulation, with no stationary period for model fitting. The key result is shown in SI Fig. 1. Qualitatively, the result is consistent: at short forecast horizons the temporal statistical model makes a better forecast while at longer forecast horizons the spatial model does better. However, as we explain in the main text (LINES), the forecast from the temporal model is not as accurate, even at short forecast horizons, as in the original simulation with a stationary period for model fitting. We believe this reflects that fact that the temporal statistical model does not account for the long-term trend. Doing so might recover the same kind of information about slow processes contained in the spatial statistical model.

I also had a quick look at the code. Unfortunately, it's written so as not to be usable by anyone other then the authors, or someone working on a Windows computer who wants to set up the same directory structure. Please, make the code portable. I would suggest making an R package, as this will give you a consistent structure, means you don't need to use setwd() and rm(list=ls()) (both abominations in portable code), and you can write vignettes which are human readable to demonstrate how the code was used to run the simulations.

RESPONSE: Ethan? Would it be rude to point out that the code uses relative paths, so you don't need to "create" a directory structure? You just download, read the readme, and set one path?

### 2020-04-28 doc/response_2_reviews_Ecography1.txt

Beyond the writing, I think one important issue is the assumption of stationarity. My guess (and I have to guess, because we're not given this information) the spatial data is taken after the simulation has run to equilibrium. But what happens if the spatial data is taken when the climate is changing? I think that would be the important question for researchers using space-for-time with contemporary data.

RESPONSE: Interesting question! We modified our code for the community turnover example to study the situation in which temperature increases through the entire simulation, with no stationary period for model fitting. The key result is shown in SI Fig. 1. Qualitatively, the result is consistent: at short forecast horizons the temporal statistical model makes a better forecast while at longer forecast horizons the spatial model does better. However, as we explain in the main text (LINES), the forecast from the temporal model is not as accurate, even at short forecast horizons, as in the original simulation with a stationary period for model fitting. We believe this reflects that fact that the temporal statistical model does not account for the long-term trend. Doing so might recover the same kind of information about slow processes contained in the spatial statistical model.

I also had a quick look at the code. Unfortunately, it's written so as not to be usable by anyone other then the authors, or someone working on a Windows computer who wants to set up the same directory structure. Please, make the code portable. I would suggest making an R package, as this will give you a consistent structure, means you don't need to use setwd() and rm(list=ls()) (both abominations in portable code), and you can write vignettes which are human readable to demonstrate how the code was used to run the simulations.

RESPONSE: We made the following changes to the code to make it more portable: 1) We removed rm(list=ls()). 2) We now use the "here" package to set the working directory. 3) We now use the "pacman" package to install and load required R packages. 4) Where we refer readers to the url for downloading the code, we have added a note directing readers to the README file in the main directory, which contains very simple instructions for running the code. The original version of our code used relative paths, so users should not need to "set up the same directory structure." As long as the user does not change the directory structure of the zip archive we distribute, the code should run (we have asked our students to test it and it has worked on a variety of platforms).

### 2020-04-29 doc/manuscript.tex
made code portable
removed s and g from manuscript

We made forecasts based on two phenomenological statistical models, each representing processes operating at different time scales. One statistical model represents the time-series or ``temporal approach.'' We regressed interannual variation in an ecological response with interannual variation in temperature at just one site. The other statistical model relies on a space-for-time substitution, which we call the ``spatial approach'' for brevity. We regressed the mean temperature on the mean of an ecological state or rate across many sites.  We compared forecasts from both statistical models to the simulated dynamics to determine how well the two approaches performed at different forecast horizons. We also assessed the potential for combining the information available in temporal and spatial patterns by using a weighted average of the forecasts from the temporal and spatial approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal approach to best predict short-term dynamics, the spatial approach to best predict long-term dynamics, while the weighted model would show potential to provide the best forecasts at transitional, intermediate time scales. The three statistical models are described in Supporting Information (Appendix \ref{models}). Computer code for both case studies is available for reviewers online (https://drive.google.com/open?id=1aju04qtQvJmZG1mcpN-6hYBZILBhDfl2) and will be archived at Zenodo upon acceptance.

@@

Evolutionary adaptation is a key uncertainty in predicting how environmental change will impact a focal population at a given location \citep{Hoffmann2011}. Like the shifts in species composition illustrated in the previous example, shifts in genotype frequencies can also influence dynamics and forecasts at different time scales. Although shifts in genotype frequencies at the population level are analogous to changes in species composition at the community level, the mechanisms are distinct: heterozygosity and genetic recombination have no analogue at the community level. We demonstrate how these processes influence short and long-term forecasts with a standard eco-evolutionary simulation model for a hypothetical annual plant population in which fecundity is temperature dependent, and different genotypes have different temperature optima (Fig. \ref{fig:evo_evo_spatial_temporal_models}A).

@@

\noindent \textbf{Haploid Model:} Begin with a haploid model that describes the number of seeds present in a seed bank.  $N_{i,t}$ is the number of seeds of species $i$ at time $t$. The model is
\begin{align}\begin{split}
N_{1,t+1} &= s_1 [1-g_1]N_{1,t}+\frac{\lambda_1(K(t))g_1N_{1,t}}{1+ \alpha_{11}g_1N_{1,t} + \alpha_{12}g_2N_{2,t}}\\
N_{2,t+1} &= s_2 [1-g_2]N_{2,t}+\frac{\lambda_2(K(t))g_2N_{2,t}}{1+ \alpha_{21}g_1N_{1,t} + \alpha_{22}g_2N_{2,t}}
\end{split}\end{align}
where $g_{i}$ is the probability of germination for species $i$, $s_i$ is the seed survival probability, $\lambda_{i}(K(t))$ is the seed production rate per plant, and $K(t)$ is the temperature at time $t$.  Below we refer to the $\alpha_{ij}$ as intra- and inter-genotype competition coefficients.

\noindent \textbf{Diploid Model:} Consider a one-species diploid model.  The genotypes are denoted by $AA$, $Aa$, and $aa$.   The number of each genotype at time $t$ is $N_{AA}(t)$, $N_{Aa}(t)$, and $N_{aa}(t)$.  The germination rates for each genotype are $g_{AA}$, $g_{Aa}$, and $g_{aa}$.  The seed survival probability and seed production rate for genotype $AA$ are $s_{AA}$ and $\lambda_{AA}(K(t))$, respectively.  The analogous parameters for the other genotypes are similarly denoted.  The competition coefficients are denoted by $\alpha_{i,j}$, e.g., $\alpha_{AA,AA}$ or $\alpha_{AA,Aa}$.  Throughout we assume that gametes mix randomly in the population.

First consider the case where the competition coefficients are zero ($\alpha_{i,j}=0$).  Let $T$ denote the total number of gamete-pairs produced in a given year,
\begin{equation}
T = \lambda_{AA}(K(t))N_{AA}(t)g_{AA} + \lambda_{Aa}(K(t))N_{Aa}(t)g_{Aa} +\lambda_{aa}(K(t))N_{aa}(t)g_{aa}.
\end{equation}
The first term is the number of gamete-pairs produced by $AA$ individuals.  The second and third terms are the numbers of gamete-pairs produced by $Aa$ and $aa$ individuals, respectively. The proportion of $A$ gametes ($\phi_A$) and the proportion of $a$ gametes ($\phi_a$) are given by
\begin{align}\begin{split}
\phi_{A} &= \frac{\lambda_{AA}(K(t))N_{AA}(t)g_{AA}+ \frac{1}{2}\lambda_{Aa}(K(t))N_{Aa}(t)g_{Aa}}{T} \hspace{10pt} \text{and} \hspace{10pt} \phi_a = 1-\phi_{A}.
\end{split}\end{align}
Note that the $T$ in the denominator of $\phi_A$ shows up because we are computing proportions.  Combining all of these we get the dynamics for each genotype,
\begin{align}\begin{split}
N_{AA}(t+1) &= s_{AA}[1-g_{AA}]N_{AA}(t) + \phi_A^2T\\
N_{Aa}(t+1) &= s_{Aa}[1-g_{Aa}]N_{Aa}(t) + \phi_A\phi_aT\\
N_{aa}(t+1) &= s_{aa}[1-g_{aa}]N_{aa}(t) + \phi_a^2T
\end{split}\end{align}

Now consider the case where the competition coefficients are non-zero ($\alpha_{i,j}\neq0$).  Including competition changes the way in which we compute $T$, $\phi_A$, and $\phi_a$.  Specifically, because the total number of seeds produced per year by each genotypes is reduced based on intra- and inter-genotype competition, the total number of gamete-pairs becomes
\begin{align}\begin{split}
T &=  \frac{\lambda_{AA}(K(t))N_{AA}(t)g_{AA}}{1+ \alpha_{AA,AA}g_{AA}N_{AA}(t) + \alpha_{AA,Aa}g_{Aa}N_{Aa}(t)+ \alpha_{AA,aa}g_{aa}N_{aa}(t)} \\ 
&+ \frac{\lambda_{Aa}(K(t))N_{Aa}(t)g_{Aa}}{1+ \alpha_{Aa,AA}g_{AA}N_{AA}(t) + \alpha_{Aa,Aa}g_{Aa}N_{Aa}(t)+ \alpha_{Aa,aa}g_{aa}N_{aa}(t)}\\
&+\frac{\lambda_{aa}(K(t))N_{aa}(t)g_{aa}}{1+ \alpha_{aa,AA}g_{AA}N_{AA}(t) + \alpha_{aa,Aa}g_{Aa}N_{Aa}(t)+ \alpha_{aa,aa}g_{aa}N_{aa}(t)}.
\label{eqn:defineT}
\end{split}\end{align}
The first line is the number of gamete-pairs produced by $AA$ individuals after accounting for the effects of competition.  The second and third lines are the numbers of gamete-pairs produced by $Aa$ and $aa$ individuals, respectively. The proportions of $A$ gametes and $a$ gametes are 
\begin{align}\begin{split}
\phi_A &= \frac{1}{T}\frac{\lambda_{AA}(K(t))N_{AA}(t)g_{AA}}{1+ \alpha_{AA,AA}g_{AA}N_{AA}(t) + \alpha_{AA,Aa}g_{Aa}N_{Aa}(t)+ \alpha_{AA,aa}g_{aa}N_{aa}(t)} \\
&+ \frac{1}{2T}\frac{\lambda_{Aa}(K(t))N_{Aa}(t)g_{Aa}}{1+ \alpha_{Aa,AA}g_{AA}N_{AA}(t) + \alpha_{Aa,Aa}g_{Aa}N_{Aa}(t)+ \alpha_{Aa,aa}g_{aa}N_{aa}(t)}\\
\phi_a &= 1- \phi_A
\label{eqn:definePhi}
\end{split}\end{align}
Combining all of this results in the same model as above,
\begin{align}\begin{split}
N_{AA}(t+1) &= s_{AA}[1-g_{AA}]N_{AA}(t) + \phi_A^2T\\
N_{Aa}(t+1) &= s_{Aa}[1-g_{Aa}]N_{Aa}(t) + 2 \phi_A\phi_aT\\
N_{aa}(t+1) &= s_{aa}[1-g_{aa}]N_{aa}(t) + \phi_a^2T,
\end{split}\end{align}
but the definitions of $T$, $\phi_A$, and $\phi_a$ are given by equations (\ref{eqn:defineT}) and (\ref{eqn:definePhi}) .

@@

\begin{table}[htp]
	\caption{\label{tab:eco-evo-pars}Parameters and parameter values for the eco-evolutionary case study. Values are assigned at
		at the start of \texttt{genetic\_diversity\_master.R}. ``Name" refers to the variable declared in the computer code. Where appropriate, the corresponding symbols from equations in Appendix \ref{eco-evo} are shown in parentheses. }
	\centering
	\smallskip 
	\begin{tabular}{lrl}
		\hline
		Name & Values & Definition \\
		\hline
		Tstdev & 1 & Standard deviation of temperature (interannual variation) \\
		baseT & -1 & Baseline temperature \\
		deltaT & 5 & Total change in temperature \\
		baseline\_yrs & 500 & Number of years at baseline temperature used to fit statistical models \\
		warming\_yrs & 100  & Number of years over which temperature increases \\
		final\_yrs & 300  & Number of years at steady-state, elevated temperature \\
		\hline
		fec\_Tmu & -1,0,1  & Optimal fecundity temperature for genotypes AA, Aa, and aa \\
		fec\_Tsigma & 8  & Standard deviation in fecundity for all genotypes \\
		fec\_max & 100 &  Maximum fecundity for all genotypes \\
		G ($g$) & 1 & Germination rate for all genotypes \\
		seedSurv ($s$)  &  0.5  & Survival rate for ungerminated seeds of all genotypes \\
		alpha ($\alpha$) & 1  &  All competition coefficients for all genotypes \\
		\hline

>>>>

We made forecasts based on two phenomenological statistical models, each representing processes operating at different time scales. One statistical model represents the time-series or ``temporal approach.'' We regressed interannual variation in an ecological response with interannual variation in temperature at just one site. The other statistical model relies on a space-for-time substitution, which we call the ``spatial approach'' for brevity. We regressed the mean temperature on the mean of an ecological state or rate across many sites.  We compared forecasts from both statistical models to the simulated dynamics to determine how well the two approaches performed at different forecast horizons. We also assessed the potential for combining the information available in temporal and spatial patterns by using a weighted average of the forecasts from the temporal and spatial approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal approach to best predict short-term dynamics, the spatial approach to best predict long-term dynamics, while the weighted model would show potential to provide the best forecasts at transitional, intermediate time scales. The three statistical models are described in Supporting Information (Appendix \ref{models}). Computer code for both case studies is available for reviewers online (https://drive.google.com/open?id=1aju04qtQvJmZG1mcpN-6hYBZILBhDfl2) and will be archived at Zenodo upon acceptance. Instructions for running the code are in the README file in the main directory of the zip archive.

@@

Evolutionary adaptation is a key uncertainty in predicting how environmental change will impact a focal population at a given location \citep{Hoffmann2011}. Like the shifts in species composition illustrated in the previous example, shifts in genotype frequencies can also influence dynamics and forecasts at different time scales. Although shifts in genotype frequencies at the population level are analogous to changes in species composition at the community level, the mechanisms are distinct: heterozygosity and genetic recombination have no analogue at the community level. We demonstrate how these processes influence short and long-term forecasts with a standard eco-evolutionary simulation model for a hypothetical annual plant population in which fecundity is temperature dependent, and different genotypes have different temperature optima (Fig. \ref{fig:evo_evo_spatial_temporal_models}A). All seeds germinate every year, preventing a seedbank from developing.

@@

\noindent \textbf{Haploid Model:} Begin with a haploid model that describes the number of seeds present in a population. We model a scenario in which all seeds germinate, so we can ignore seedbank dynamics.  $N_{i,t}$ is the number of seeds of species $i$ at time $t$. The model is
\begin{align}\begin{split}
N_{1,t+1} &= \frac{\lambda_1(K(t))N_{1,t}}{1+ \alpha_{11}N_{1,t} + \alpha_{12}N_{2,t}}\\
N_{2,t+1} &= \frac{\lambda_2(K(t))N_{2,t}}{1+ \alpha_{21}N_{1,t} + \alpha_{22}N_{2,t}}
\end{split}\end{align}
where $\lambda_{i}(K(t))$ is the seed production rate per plant, and $K(t)$ is the temperature at time $t$.  Below we refer to the $\alpha_{ij}$ as intra- and inter-genotype competition coefficients.

%\noindent \textbf{Diploid Model:} Consider a one-species diploid model.  The genotypes are denoted by $AA$, $Aa$, and $aa$.   The number of each genotype at time $t$ is $N_{AA}(t)$, $N_{Aa}(t)$, and $N_{aa}(t)$.  The germination rates for each genotype are $g_{AA}$, $g_{Aa}$, and $g_{aa}$.  The seed survival probability and seed production rate for genotype $AA$ are $s_{AA}$ and $\lambda_{AA}(K(t))$, respectively.  The analogous parameters for the other genotypes are similarly denoted.  The competition coefficients are denoted by $\alpha_{i,j}$, e.g., $\alpha_{AA,AA}$ or $\alpha_{AA,Aa}$.  Throughout we assume that gametes mix randomly in the population.

\noindent \textbf{Diploid Model:} Consider a one-species diploid model.  The genotypes are denoted by $AA$, $Aa$, and $aa$. The number of each genotype at time $t$ is $N_{AA}(t)$, $N_{Aa}(t)$, and $N_{aa}(t)$.  
%The germination rates for each genotype are $g_{AA}$, $g_{Aa}$, and $g_{aa}$.  
%The seed survival probability and %
The seed production rate for genotype $AA$ is $\lambda_{AA}(K(t))$, and the analogous parameters for the other genotypes are similarly denoted.  The competition coefficients are denoted by $\alpha_{i,j}$, e.g., $\alpha_{AA,AA}$ or $\alpha_{AA,Aa}$.  Throughout we assume that gametes mix randomly in the population.

First consider the case where the competition coefficients are zero ($\alpha_{i,j}=0$).  Let $T$ denote the total number of gamete-pairs produced in a given year,
\begin{equation}
T = \lambda_{AA}(K(t))N_{AA}(t) + \lambda_{Aa}(K(t))N_{Aa}(t) +\lambda_{aa}(K(t))N_{aa}(t).
\end{equation}
The first term is the number of gamete-pairs produced by $AA$ individuals.  The second and third terms are the numbers of gamete-pairs produced by $Aa$ and $aa$ individuals, respectively. The proportion of $A$ gametes ($\phi_A$) and the proportion of $a$ gametes ($\phi_a$) are given by
\begin{align}\begin{split}
\phi_{A} &= \frac{2\lambda_{AA}(K(t))N_{AA}(t)+ \lambda_{Aa}(K(t))N_{Aa}(t)}{2T} \hspace{10pt} \text{and} \hspace{10pt} \phi_a = 1-\phi_{A}.
\end{split}\end{align}
Note that the $T$ in the denominator of $\phi_A$ shows up because we are computing proportions.  Combining all of these we get the dynamics for each genotype,
\begin{align}\begin{split}
N_{AA}(t+1) &= \phi_A^2T\\
N_{Aa}(t+1) &= \phi_A\phi_aT\\
N_{aa}(t+1) &= \phi_a^2T
\end{split}\end{align}

Now consider the case where the competition coefficients are non-zero ($\alpha_{i,j}\neq0$).  Including competition changes the way in which we compute $T$, $\phi_A$, and $\phi_a$.  Specifically, because the total number of seeds produced per year by each genotypes is reduced based on intra- and inter-genotype competition, the total number of gamete-pairs becomes
\begin{align}\begin{split}
T &=  \frac{\lambda_{AA}(K(t))N_{AA}(t)}{1+ \alpha_{AA,AA}N_{AA}(t) + \alpha_{AA,Aa}N_{Aa}(t)+ \alpha_{AA,aa}N_{aa}(t)} \\ 
&+ \frac{\lambda_{Aa}(K(t))N_{Aa}(t)}{1+ \alpha_{Aa,AA}N_{AA}(t) + \alpha_{Aa,Aa}N_{Aa}(t)+ \alpha_{Aa,aa}N_{aa}(t)}\\
&+\frac{\lambda_{aa}(K(t))N_{aa}(t)}{1+ \alpha_{aa,AA}N_{AA}(t) + \alpha_{aa,Aa}N_{Aa}(t)+ \alpha_{aa,aa}N_{aa}(t)}.
\label{eqn:defineT}
\end{split}\end{align}
The first line is the number of gamete-pairs produced by $AA$ individuals after accounting for the effects of competition.  The second and third lines are the numbers of gamete-pairs produced by $Aa$ and $aa$ individuals, respectively. The proportions of $A$ gametes and $a$ gametes are 
\begin{align}\begin{split}
\phi_A &= \frac{2}{2T}\frac{\lambda_{AA}(K(t))N_{AA}(t)}{1+ \alpha_{AA,AA}N_{AA}(t) + \alpha_{AA,Aa}N_{Aa}(t)+ \alpha_{AA,aa}N_{aa}(t)} \\
&+ \frac{1}{2T}\frac{\lambda_{Aa}(K(t))N_{Aa}(t)}{1+ \alpha_{Aa,AA}N_{AA}(t) + \alpha_{Aa,Aa}N_{Aa}(t)+ \alpha_{Aa,aa}N_{aa}(t)}\\
\phi_a &= 1- \phi_A
\label{eqn:definePhi}
\end{split}\end{align}
Combining all of this results in the same model as above,
\begin{align}\begin{split}
N_{AA}(t+1) &= \phi_A^2T\\
N_{Aa}(t+1) &= 2 \phi_A\phi_aT\\
N_{aa}(t+1) &= \phi_a^2T,
\end{split}\end{align}
but the definitions of $T$, $\phi_A$, and $\phi_a$ are given by equations (\ref{eqn:defineT}) and (\ref{eqn:definePhi}) .

@@

\begin{table}[htp]
	\caption{\label{tab:eco-evo-pars}Parameters and parameter values for the eco-evolutionary case study. Values are assigned at
		at the start of \texttt{genetic\_diversity\_master.R}. ``Name" refers to the variable declared in the computer code. Where appropriate, the corresponding symbols from equations in Appendix \ref{eco-evo} are shown in parentheses. }
	\centering
	\smallskip 
	\begin{tabular}{lrl}
		\hline
		Name & Values & Definition \\
		\hline
		Tstdev & 1 & Standard deviation of temperature (interannual variation) \\
		baseT & -1 & Baseline temperature \\
		deltaT & 5 & Total change in temperature \\
		baseline\_yrs & 500 & Number of years at baseline temperature used to fit statistical models \\
		warming\_yrs & 100  & Number of years over which temperature increases \\
		final\_yrs & 300  & Number of years at steady-state, elevated temperature \\
		\hline
		fec\_Tmu & -1,0,1  & Optimal fecundity temperature for genotypes AA, Aa, and aa \\
		fec\_Tsigma & 8  & Standard deviation in fecundity for all genotypes \\
		fec\_max & 100 &  Maximum fecundity for all genotypes \\
		alpha ($\alpha$) & 1  &  All competition coefficients for all genotypes \\
		\hline
